### 2024-10-29 paper/5-eval.tex
Add space

\red{TODO: Change to array} \\
\red{TODO: Change naming for $c$}
\begin{align}
  &c^* \vdash call(\$brAndReturning); ~ Enter ~ (n, c)
  \label{eq:resolve-1} \\
  &\leadsto c^* \vdash \epsilon; ~ Al ~ ([ ~ \pushctxi, \enteri ~ ], 0, ~ Enter ~ (n, c))
  \label{eq:resolve-2} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~ Al ~ ([ ~ \enteri ~ ], 1, ~ Enter ~ (n, c))
  \label{eq:resolve-3} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (br ~ 0), ~ (unreachable), ~ (end ~ 2); ~
    Enter ~ (2, Al ~ (\epsilon, 0, ~ Enter ~ (n, c)))
  \label{eq:resolve-4} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (unreachable), ~ (end ~ 2); \\
  &\quad\quad Al ~ ([ ~ \red{\symbol{PopCtxI}}, ~ \executeseqi ~ ], ~ 0, ~ Enter ~ (2, Al ~ (\epsilon, 0, ~ Enter ~ (n, c))))
  \label{eq:resolve-5} \\
  &\leadsto Frame, ~ c^* \vdash (end ~ 1); ~
    Al ~ ([ ~ \executeseqi ~ ], ~ 0, ~ Enter ~ (1, Al ~ (\epsilon, 0, ~ Enter ~ (n, c))))
  \label{eq:resolve-6} \\
  &\leadsto Frame, ~ c^* \vdash (end ~ 1); ~
    Al ~ (\epsilon, ~ 0, ~ Enter ~ (1, Al ~ (\epsilon, 0, ~ Enter ~ (n, c))))
  \label{eq:resolve-7} \\
  &\leadsto Frame, ~ c^* \vdash (end ~ 1); ~ Enter ~ (1, Al ~ (\epsilon, 0, ~ Enter ~ (n, c)))
  \label{eq:resolve-8} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~
    Al ~ ([ ~ \red{\symbol{PopCtx}} ~ ], ~ 0, ~ Enter ~ (0, Al ~ (\epsilon, 0, ~ Enter ~ (n, c))))
  \label{eq:resolve-9} \\
  &\leadsto c^* \vdash \epsilon; ~
    Al ~ (\epsilon, ~ 0, ~ Enter ~ (0, Al ~ (\epsilon, 0, ~ Enter ~ (n, c))))
  \label{eq:resolve-10} \\
  &\leadsto c^* \vdash \epsilon; ~ Enter ~ (0, Al ~ (\epsilon, 0, ~ Enter ~ (n, c)))
  \label{eq:resolve-11} \\
  &\leadsto c^* \vdash \epsilon; ~ Al ~ (\epsilon, 0, ~ Enter ~ (n, c))
  \label{eq:resolve-12} \\
  &\leadsto c^* \vdash \epsilon; ~ Enter ~ (n, c)
  \label{eq:resolve-13}
\end{align}

>>>>

\red{TODO: Change to array} \\
\red{TODO: Change naming for $c$}
\begin{align}
  &c^* \vdash call(\$brAndReturning); ~ \wasm ~ (n, ~ c)
  \label{eq:resolve-1} \\
  &\leadsto c^* \vdash \epsilon; ~ \al ~ ([ ~ \pushctxi, ~ \enteri ~ ], ~ 0, ~ \wasm ~ (n, ~ c))
  \label{eq:resolve-2} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~ \al ~ ([ ~ \enteri ~ ], ~ 1, ~ \wasm ~ (n, ~ c))
  \label{eq:resolve-3} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (br ~ 0), ~ (unreachable), ~ (end ~ 2); ~
    \wasm ~ (2, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c)))
  \label{eq:resolve-4} \\
  &\leadsto Label(\epsilon), ~ Frame, ~ c^* \vdash (unreachable), ~ (end ~ 2); \\
  &\quad\quad \al ~ ([ ~ \red{\symbol{PopCtxI}}, ~ \executeseqi ~ ], ~ 0, ~ \wasm ~ (2, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c))))
  \label{eq:resolve-5} \\
  &\leadsto Frame, ~ c^* \vdash (end ~ 1); ~
    \al ~ ([ ~ \executeseqi ~ ], ~ 0, ~ \wasm ~ (1, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c))))
  \label{eq:resolve-6} \\
  &\leadsto Frame, ~ c^* \vdash (end ~ 1); ~
    \al ~ (\epsilon, ~ 0, ~ \wasm ~ (1, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c))))
  \label{eq:resolve-7} \\
  &\leadsto Frame, ~ c^* \vdash (end ~ 1); ~ \wasm ~ (1, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c)))
  \label{eq:resolve-8} \\
  &\leadsto Frame, ~ c^* \vdash \epsilon; ~
    \al ~ ([ ~ \red{\symbol{PopCtx}} ~ ], ~ 0, ~ \wasm ~ (0, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c))))
  \label{eq:resolve-9} \\
  &\leadsto c^* \vdash \epsilon; ~
    \al ~ (\epsilon, ~ 0, ~ \wasm ~ (0, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c))))
  \label{eq:resolve-10} \\
  &\leadsto c^* \vdash \epsilon; ~ \wasm ~ (0, ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c)))
  \label{eq:resolve-11} \\
  &\leadsto c^* \vdash \epsilon; ~ \al ~ (\epsilon, ~ 0, ~ \wasm ~ (n, ~ c))
  \label{eq:resolve-12} \\
  &\leadsto c^* \vdash \epsilon; ~ \wasm ~ (n, ~ c)
  \label{eq:resolve-13}
\end{align}
